---
title: "Exploration"
author: "Kaz Sakamoto"
output: 
    html_document:
        toc: yes
        toc_float:
            collapsed: no
            smooth_scoll: yes
        number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, cache = TRUE)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(sf)
library(leaflet)
## here we are going to find the root_file 
root <- rprojroot::find_rstudio_root_file()
## we are going to set the data file path here
dataDir <- file.path(root, 'data')
shapeDir <- file.path(root, 'shape')
```

# Whole Foods



Here is the location for the two Whole Foods locations
```{r}
wf <- tibble(lat = c(40.8076461,40.6749728),
             long = c(-73.9483658,-73.9882083), 
             store = c("Whole Foods Harlem", "Whole Foods Gowanus"))
wholeFoods<- wf %>% st_as_sf(coords = c("long","lat"), crs = 4326)
```

# Sales Data

This is the compelte rolling sales data between 2010-2019

```{r}
allSales <- readr::read_csv(file.path(dataDir, "rollingSales/nycSales_2010_2019"))
```

Here is a little bit of cleaning of the data

```{r}
resSales <- allSales %>% filter(str_detect(`BUILDING CLASS AT TIME OF SALE`,pattern = "[A,B,C,D]")) %>% 
    mutate(`SALE DATE` = as_date(`SALE DATE`),
           borough_name = case_when(BOROUGH == 1 ~ "Manhattan",
                                    BOROUGH == 2 ~ "Bronx",
BOROUGH == 3 ~ "Brooklyn",
BOROUGH == 4 ~ "Queens",
BOROUGH == 5 ~ "Staten Island")) %>% janitor::clean_names() %>% 
    mutate(year = year(sale_date),
                    month = month(sale_date),
                    borough = as.factor(borough))
rm(allSales)
```

here is a brek down of the median price for residential units across boroughs and dates

```{r}
resSales %>%
    filter(sale_price > 10000, residential_units < 3, residential_units > 0) %>% 
    group_by(borough, month, year,residential_units) %>% summarize(priceMean = mean(sale_price),
                                                 priceMed = median(sale_price),
                                                 date = min(sale_date)) %>% 
    ggplot(aes(x = date, y = priceMed,color = borough)) + 
    geom_point() +
    geom_line() + 
    facet_grid(borough~residential_units, scales = "free_y") + 
    theme_minimal()
```

# Census Tracts and Sales

```{r}
nyct <- st_read(file.path(shapeDir,'nyct2010'))


nyct <- nyct %>% mutate(geo_county  = case_when(BoroName == 'Bronx' ~ '005',
                                                BoroName == 'Brooklyn' ~ '047',
                                                BoroName == 'Manhattan' ~ '061',
                                                BoroName == 'Queens' ~ '081',
                                                BoroName == 'Staten Island' ~ '085',
                                                TRUE ~ 'Other'),
                        geo_fips = paste0("36", geo_county, CT2010)) %>% janitor::clean_names()
```

```{r}
acs2018 <- readr::read_csv(file.path(dataDir, "acs20185yr.csv"))

acs2018 <- acs2018 %>% 
    janitor::clean_names() %>% 
    mutate(geo_fips = as.character(geo_fips))

```

```{r}
# 
# placeTotal <- readr::read_csv(file.path(dataDir, "placesTotal.csv")) %>% 
#     st_as_sf(coords = c("long","lat"), crs = 4326) %>% 
#     st_transform(2263)
# 
# placeTotal <- st_join(placeTotal, nyct)
# 
```

```{r}
# 
# resSales <- resSales %>% left_join(placeTotal %>% st_drop_geometry())
# 
# resSales %>% 
#     filter(!is.na(puma)) %>% 
#     group_by(borough_name, puma, year) %>% 
#     summarize(medPrice = median(sale_price),
#               avgPrice = mean(sale_price),
#               count = n()) %>% 
#     ggplot(aes(year, medPrice, color = medPrice)) +
#     geom_point() + 
#     facet_wrap(~puma)
```

# Census Tracts Demographics

```{r}
nyct <- nyct %>% left_join(acs2018)
```

```{r}
# palPrice <- colorNumeric( palette = "Reds",
#                             domain = placeTotal$sale_price)
palValue <- colorNumeric( palette = "Reds",
                            domain = nyct$median_value)
leaflet(options = leafletOptions(zoomControl = TRUE)) %>% 
    addPolygons(data = nyct %>% st_transform(4326), 
                        stroke = .4,
                        color = ~palValue(median_value),
                        label = ~median_value,
                        group = "medianValue") %>% 
            setView(lat = 40.7445698, lng = -73.9375989, zoom = 12) %>% 
            addProviderTiles(providers$CartoDB.DarkMatter) %>% 
            # addCircleMarkers(data = placeJoin, 
            #                  stroke = .5, radius = 3,color = ~palPrice(sale_price),
            #                  label = ~address,
            #                  group = "Sales")  %>% 
        addLayersControl(
            overlayGroups = c("medianValue", "Sales"),
            options = layersControlOptions(collapsed = FALSE)
        )
    
```

# Census Block Groups Demographics

```{r}
nybg <- st_read(file.path(shapeDir,'nycb2010'))


nybg <- nybg %>% mutate(geo_county  = case_when(BoroName == 'Bronx' ~ '005',
                                                BoroName == 'Brooklyn' ~ '047',
                                                BoroName == 'Manhattan' ~ '061',
                                                BoroName == 'Queens' ~ '081',
                                                BoroName == 'Staten Island' ~ '085',
                                                TRUE ~ 'Other'),
                        blockGroup = stringr::str_sub(CB2010,start = 1,1),
                        geo_fips = paste0("36", geo_county, CT2010, blockGroup)) %>% janitor::clean_names()

# nybg <- nybg %>% st_buffer(0) %>% 
#     group_by(geo_fips) %>% 
#   summarize(geometry = st_union(geometry))
```
<!-- url:  -->
<!-- https://www.socialexplorer.com/tables/ACS2018_5yr/R12555664 -->
```{r}

acsbg2018 <- readxl::read_xls(file.path(dataDir, "acs20185yrBlockGroup.xls"))
acsbg2018 <- acsbg2018 %>% 
    janitor::clean_names() %>% 
    mutate(geo_fips = as.character(geo_fips))

```

<!-- url: -->
<!-- https://www.socialexplorer.com/tables/ACS2014_5yr/R12555594 -->

```{r}

acsbg2014 <- readxl::read_xls(file.path(dataDir, "acs20145yrBlockGroup.xls"))
acsbg2014 <- acsbg2014 %>% 
    janitor::clean_names() %>% 
    mutate(geo_fips = as.character(geo_fips))

```

```{r}
acsbg2014Value <- acsbg2014 %>% select(geo_fips,median_value) %>% 
    rename(median_value2014 = median_value)
nybgJoin <- nybg %>% left_join(acsbg2018) %>% 
    left_join(acsbg2014Value)
nybgJoin <- nybgJoin %>% mutate(medValueDiff = median_value - median_value2014)
```

```{r}
palValue2014 <- colorNumeric( palette = "Reds",
                            domain = nybgJoin$median_value2014)


palValue2018 <- colorNumeric( palette = "Reds",
                            domain = nybgJoin$median_value)

palChange <- colorNumeric(palette = "RdYlGn",
                          domain = nybgJoin$medValueDiff)

leaflet(data = nybgJoin %>% st_transform(4326), 
        options = leafletOptions(zoomControl = TRUE)) %>% 
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
    setView(lat = 40.7445698, lng = -73.9375989, zoom = 12) %>% 
    addPolygons(
        stroke = .3,
        color = ~palValue2018(median_value),
        label = ~median_value,
        group = "Median Value 2018") %>% 
    
    addPolygons( 
        stroke = .3,
        color = ~palValue2014(median_value2014),
        label = ~median_value2014,
        group = "Median Rent")  %>% 
        addPolygons( 
        stroke = .3,
        color = ~palChange(medValueDiff),
        label = ~medValueDiff,
        group = "Median Value Change") %>%
  addLegend("bottomright", pal = palChange, values = ~medValueDiff,
    title = "Median Value Change",
    labFormat = labelFormat(prefix = "$"),
    opacity = 1
  ) %>%  
    addMarkers(data = wholeFoods,label = ~store) %>% 
    addLayersControl(
        baseGroups  = c("Median Value", "Median Rent","Median Value Change"),
        options = layersControlOptions(collapsed = FALSE)
    )
    
```

# Cultural Institutions

```{r}
facilities <-  st_read(file.path(shapeDir, "facilities_2019")) %>% janitor::clean_names()

CIFilters <-c("ACADEMIC AND SPECIAL LIBRARIES",
              "MUSEUMS", "PUBLIC LIBRARIES")

CI <- facilities %>% filter(facsubgrp %in% CIFilters) 

```


# Parks

```{r}
parkFilters <- c("PRIVATELY OWNED PUBLIC SPACE",
                 "RECREATION AND WATERFRONT SITES", 
                 "PARKS")

parks <- facilities %>% filter(facsubgrp %in% parkFilters) 
rm(facilities)
```

# DOB Permits 
```{r}
permits <- readr::read_csv(file.path(dataDir, "DOB_Permit_Issuance2010_2020.csv")) %>% 
    janitor::clean_names()
permits <- permits %>% 
    select(borough, job_type,
           block, lot, permit_type,
           filing_date, latitude, longitude)

permits <- permits %>% 
    mutate(filing_date = lubridate::mdy_hms(filing_date),
           year = lubridate::year(filing_date),
           month = lubridate::month(filing_date))

permits %>% group_by(borough, month, year) %>% 
    summarize(date = min(filing_date),
              count = n()) %>% 
    ggplot(aes(date, count)) +
    geom_point(aes(color = borough)) +
    geom_smooth() + 
    facet_wrap(~borough) +
    theme(legend.position = "none")
```


## Whole Foods Analysis
```{r}
wholeFoods1mBuffer <- st_buffer(wholeFoods %>% st_transform(2263), dist = 5280)
```
nyc block group intersect
```{r}
nyctJoin <- st_join(nyct, wholeFoods1mBuffer)
nyctJoin %>% filter(!is.na(store))
```

```{r}
resdf <- readr::read_csv(file.path(dataDir, "nyc_Sales2010_2020geocoded.csv"))
resdf <- resSales %>% left_join(resdf)
resdf <- resdf %>% filter(!is.na(lat))

resShape <- resdf %>% st_as_sf(crs =4326, coords =  c("long", "lat")) %>% 
    st_transform(2263)
resShapeJoin <- st_join(resShape, nyctJoin)

```


```{r}
resShapeJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
      filter(!(abs(sale_price - median(sale_price)) > 4*sd(sale_price))) %>% 
    mutate(quart = quarter(sale_date,with_year = FALSE),
            borough_name = as.character(borough_name),
            vistype = if_else(is.na(store), borough_name, 
                  if_else(store == "Whole Foods Harlem", "WF Harlem", borough_name))) %>% 
    group_by(vistype, quart, year,residential_units) %>% 
    summarize(priceMean = mean(sale_price),
              priceMed = median(sale_price),
              date = min(sale_date)) %>% 
    filter(priceMed > 0) %>% 
    ggplot(aes(x = date, y = priceMed)) + 
    geom_point(aes(color = vistype)) +
    geom_line(aes(color = vistype)) +
    geom_smooth() +    
    facet_wrap(~vistype, scales = "free_y") + 
    theme_minimal()
```

```{r}
resShapeJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
      filter(!(abs(sale_price - median(sale_price)) > 4*sd(sale_price))) %>% 
    mutate(quart = quarter(sale_date,with_year = FALSE),
            borough_name = as.character(borough_name),
            vistype = if_else(is.na(store), borough_name, 
                  if_else(store == "Whole Foods Harlem", "WF Harlem", borough_name))) %>% 
    group_by(vistype, year) %>% 
    summarize(priceMed = median(sale_price)) %>% 
    ungroup() %>% 
    tidyr::pivot_wider(names_from = year,values_from = priceMed)
```


```{r}
resShapeJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
    mutate(boro_ct2010 = as.character(boro_ct2010)) %>% 
    group_by(boro_ct2010, year) %>%
    summarize(priceMed = median(sale_price)) %>% 
    ungroup() %>% 
    tidyr::pivot_wider(names_from = year,values_from = priceMed)
    
```


```{r}
medianPriceCT <- resShapeJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
    mutate(boro_ct2010 = as.character(boro_ct2010)) %>% 
    group_by(boro_ct2010) %>%
    summarize(priceMed = median(sale_price)) %>% 
    ungroup()
nyct <- st_read(file.path(shapeDir,'nyct2010'))


nyct <- nyct %>% mutate(geo_county  = case_when(BoroName == 'Bronx' ~ '005',
                                                BoroName == 'Brooklyn' ~ '047',
                                                BoroName == 'Manhattan' ~ '061',
                                                BoroName == 'Queens' ~ '081',
                                                BoroName == 'Staten Island' ~ '085',
                                                TRUE ~ 'Other'),
                        geo_fips = paste0("36", geo_county, CT2010)) %>% janitor::clean_names()
nyct <- nyct %>% left_join(medianPriceCT)
```

```{r}
nyct$scaledPrice <- scale(nyct$priceMed)
palmedPrice <- colorNumeric(palette = "Reds",
                          domain = nyct$scaledPrice)

leaflet(data = nyct %>% st_transform(4326), 
        options = leafletOptions(zoomControl = TRUE)) %>% 
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
    setView(lat = 40.7445698, lng = -73.9375989, zoom = 12) %>% 
    addPolygons(
        stroke = .2,
        fillColor = ~palmedPrice(scaledPrice),
        color = ~palmedPrice(scaledPrice),
        fillOpacity = .5,
        label = ~priceMed,
        group = "Sales Median Price") 
```

nyc block group intersect
```{r}
nybgJoin <- st_join(nybg, wholeFoods1mBuffer)
nybgJoin %>% filter(!is.na(store))
```

```{r}
resBGJoin <- st_join(resShape, nybgJoin)
```


```{r}
resBGJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
      filter(!(abs(sale_price - median(sale_price)) > 4*sd(sale_price))) %>% 
    mutate(quart = quarter(sale_date,with_year = FALSE),
            borough_name = as.character(borough_name),
            vistype = if_else(is.na(store), borough_name, 
                  if_else(store == "Whole Foods Harlem", "WF Harlem", borough_name))) %>% 
    group_by(vistype, quart, year,residential_units) %>% 
    summarize(priceMean = mean(sale_price),
              priceMed = median(sale_price),
              date = min(sale_date)) %>% 
    filter(priceMed > 0) %>% 
    ggplot(aes(x = date, y = priceMed)) + 
    geom_point(aes(color = vistype)) +
    geom_line(aes(color = vistype)) +
    geom_smooth() +    
    facet_wrap(~vistype, scales = "free_y") + 
    theme_minimal()
```

```{r}
resBGJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
      filter(!(abs(sale_price - median(sale_price)) > 4*sd(sale_price))) %>% 
    mutate(quart = quarter(sale_date,with_year = FALSE),
            borough_name = as.character(borough_name),
            vistype = if_else(is.na(store), borough_name, 
                  if_else(store == "Whole Foods Harlem", "WF Harlem", borough_name))) %>% 
    group_by(vistype, year) %>% 
    summarize(priceMed = median(sale_price)) %>% 
    ungroup() %>% 
    tidyr::pivot_wider(names_from = year,values_from = priceMed)
```


```{r}
resBGJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
    mutate(bctcb2010 = as.character(bctcb2010)) %>% 
    group_by(bctcb2010, year) %>%
    summarize(priceMed = median(sale_price)) %>% 
    ungroup() %>% 
    tidyr::pivot_wider(names_from = year,values_from = priceMed)
    
```


```{r}
medianPriceCB <- resBGJoin %>% 
    st_drop_geometry() %>%
    filter(sale_price > 10000,residential_units < 3) %>% 
    mutate(bctcb2010 = as.character(bctcb2010)) %>% 
    group_by(bctcb2010) %>%
    summarize(priceMed = median(sale_price)) %>% 
    ungroup()

nybg <- nybg %>% left_join(medianPriceCB)
```

```{r}
nybg$scaledPrice <- scale(nybg$priceMed)
palmedPrice <- colorNumeric(palette = "Reds",
                          domain = nybg$scaledPrice)

leaflet(data = nybg %>% st_transform(4326), 
        options = leafletOptions(zoomControl = TRUE)) %>% 
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
    setView(lat = 40.7445698, lng = -73.9375989, zoom = 12) %>% 
    addPolygons(
        stroke = .2,
        fillColor = ~palmedPrice(scaledPrice),
        color = ~palmedPrice(scaledPrice),
        fillOpacity = .5,
        label = ~priceMed,
        group = "Sales Median Price") 
```

# Distanaces

```{r}
nearDist <- function(property, features){
    # print(st_crs(features))
    # print(st_crs(property))
    nearFeature <- features[st_nearest_feature(property, features),]
    distance <- st_distance(property, nearFeature)
    return(distance)
}
```

```{r}
# CIDist <- split(resShape[,"geometry"], seq(nrow(resShape))) %>% purrr::map_dbl(~nearDist(.x, CI))
# parksDist <- split(resShape[,"geometry"], seq(nrow(resShape))) %>% purrr::map_dbl(~nearDist(.x, parks))

# distDF <- tibble(CIDist,parksDist)
# readr::write_csv(distDF,"distDF.csv")

# subways <- st_read(file.path(shapeDir,"SubwayEntrances")) %>% st_transform(2263)
# SubwayDist <- split(resShape[,"geometry"], seq(nrow(resShape))) %>% purrr::map_dbl(~nearDist(.x, subways))

subwayDistDF <- tibble(SubwayDist)
readr::write_csv(subwayDistDF, "subwayDist.csv")
```


