---
title: "DataPrep"
author: "Kaz"
date: "11/19/2020"
output: 
    html_document:
        toc: yes
        toc_float:
            collapsed: no
            smooth_scoll: yes
        number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
shapeDir <- file.path(root, 'shape')
library(dplyr)
library(readxl)
library(purrr)
library(sf)
library(readr)
library(stringr)
library(lubridate)
library(ggplot2)
library(tmap)
```

## Loading Data

```{r}
wf <- st_read(file.path(shapeDir, "wholeFoods"))
wfHarlem <- wf %>% filter(store == "Whole Foods Harlem") %>% st_transform(2263)
wfHarlemBufferHalf <- wfHarlem %>% st_buffer(2640)
wfHarlemBufferOne <- wfHarlem %>% st_buffer(2640*2)

```

```{r}
pluto <- st_read(file.path(shapeDir, "PLUTO_Dissolve")) %>% filter(Borough == "MN")
```

```{r}
tm_shape(pluto, bbox = st_bbox(wfHarlemBufferOne)) +
    tm_polygons() +
    tm_shape(wfHarlemBufferHalf) +
    tm_borders() +
    tm_shape(wfHarlemBufferOne) +
    tm_borders() +
    tm_shape(wfHarlem) +
    tm_symbols()
```

```{r}
plutoWF <- pluto %>% filter(st_intersects(pluto, wfHarlemBufferOne,sparse = FALSE)) %>% 
    select(BoroName, Block) %>% 
    group_by(Block) %>% 
    summarize(BoroName = first(BoroName)) %>% 
    st_cast() %>% 
    ungroup()
plutoWF <- plutoWF %>% 
    filter(!Block %in% c(1111, 1897)) %>% 
    sf::st_join(wfHarlemBufferHalf %>%mutate(buffer = "Half"),join =st_within) %>%  
    dplyr::mutate(buffer = if_else(is.na(buffer), "Mile", buffer))

tm_shape(plutoWF) + 
    tm_polygons(col = "buffer")
```

## Permits

```{r}
permits <- read_csv(file.path(dataDir, "DOB_Permit_Issuance2010_2020.csv"))

permits <- permits %>% 
    janitor::clean_names()%>% 
    select(borough, job_type,
           block, lot, permit_type,
           filing_date, latitude, longitude)

permits <- permits %>% 
    mutate(filing_date = lubridate::mdy_hms(filing_date),
           year = lubridate::year(filing_date),
           month = lubridate::month(filing_date))

permitsMN <- permits %>% filter(borough == "MANHATTAN")
rm(permits)

permitsWF <- permitsMN %>% mutate(Block = as.numeric(block)) %>% 
                         left_join(plutoWF %>% st_drop_geometry()) %>% 
    filter(!is.na(buffer))
```

```{r}
permitsWF %>% 
    group_by( month, year, buffer) %>% 
    summarize(date = min(filing_date),
              count = n()) %>% 
    ggplot(aes(date, count)) +
    geom_point(aes(color = buffer)) +
    geom_smooth(aes(color = buffer)) + 
    #facet_wrap(~buffer) +
    theme(legend.position = "none")
```


## Sales

```{r}
sales <- read_csv(file.path(dataDir, "rollingSales","nycSales_2010_2019"))

mnSales <- sales %>% filter(BOROUGH == 1) %>% janitor:::clean_names()
rm(sales)
```

```{r}
# mnSalesJoin <- plutoWF %>%     
#     janitor:::clean_names() %>% 
#     left_join(mnSales, by = c("block" = "block")) %>% 
#     tidyr::separate(address,  c("address","aptNum"), ",") %>% 
#     mutate(BL = paste0(block, stringr::str_pad(lot, 4,side = "left", pad = "0")),
#            bbl = paste0(1, stringr::str_pad(block, 5,side = "left", pad = "0"), stringr::str_pad(lot, 4,side = "left", pad = "0")),
#           aptNum = if_else(is.na(apartment_number), aptNum, apartment_number),
#           time = factor(if_else(sale_date < ymd("2017-01-01"), "Before WF", "After WF"), levels = c("Before WF", "After WF")))
```

```{r}
# library(geoclient)
# 
# mnSalesJoin <- mnSalesJoin %>% filter(nchar(bbl) == 10) %>% 
#     mutate(bbl_use = geo_bbl(bbl)[["bbl"]])
```
```{r}
mnSalesJoin <- readr::read_csv(file.path(dataDir, "mnSalesJoin.csv"))
```

## average change
```{r}
mnSalesSummary <- mnSalesJoin %>% 
    #st_drop_geometry() %>% 
    filter(sale_price > 50000) %>% 
    mutate(month = month(sale_date),
           year = year(sale_date)) %>% 
    group_by(year, buffer) %>% 
    summarize(meanSale = mean(sale_price),
              medSale = median(sale_price),
              count = n())
```
# average sale price
```{r}
mnSalesSummary %>% 
    ggplot(aes(year, meanSale)) +
    geom_point(aes(color = buffer)) +
    geom_smooth(aes(color = buffer)) 
    #facet_wrap(~buffer) +
```


```{r}
mnSalesSummary %>% 
    ggplot(aes(year, medSale)) +
    geom_point(aes(color = buffer)) +
    geom_smooth(aes(color = buffer)) 
```

```{r}
mnSalesSummary %>% 
    ggplot(aes(year, count)) +
    geom_point(aes(color = buffer)) +
    geom_smooth(aes(color = buffer)) 
```

## Repeat sales

```{r}
repeatLots <- mnSalesJoin %>% 
    #st_drop_geometry() %>% 
    filter(sale_price > 50000) %>% 
    group_by(BL, address, aptNum) %>% count() %>% 
    filter(n > 1) %>% 
    pull(BL)

mnSalesRepeat <- mnSalesJoin %>% filter(BL %in% repeatLots) %>% 
    arrange(BL)
```

```{r}
mnSalesRepeat %>% 
    #st_drop_geometry() %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price)) %>% 
    ungroup() %>% 
    filter(last < 10000000, last > 50000) %>% 
    ggplot(aes(time, last)) +
    geom_point(aes(group = BL, color = time)) +
    geom_line(aes(group = BL), alpha = .2) +
    facet_wrap(~buffer) + 
    theme_minimal()
```


```{r}
mnSalesRepeat %>% 
    #st_drop_geometry() %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present)) %>% 
    ungroup() %>% 
    filter(last < 10000000, last > 50000, class == "R4") %>% 
    ggplot(aes(time, last)) +
    geom_point(aes(group = BL, color = time)) +
    geom_line(aes(group = BL), alpha = .2) +
    facet_wrap(~buffer) + 
    theme_minimal()
```

## Avg chanage R4
```{r}
mnSalesRepeat %>% 
    #st_drop_geometry() %>% 
    filter(building_class_at_present == "R4") %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present)) %>% 
    ungroup() %>% 
    group_by(buffer,time) %>% 
    summarize(avgPrice = mean(last),
              medPrice = median(last)) %>% 
    ggplot(aes(time, avgPrice)) +
    geom_point(aes(group = buffer, color = buffer)) +
    geom_line(aes(group = buffer), alpha = .2) +
    theme_minimal()
```
## Median change R4
```{r}
mnSalesRepeat %>% 
   # st_drop_geometry() %>% 
    filter(building_class_at_present == "R4") %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present)) %>% 
    ungroup() %>% 
    group_by(buffer,time) %>% 
    summarize(avgPrice = mean(last),
              medPrice = median(last)) %>% 
    ggplot(aes(time, medPrice)) +
    geom_point(aes(group = buffer, color = buffer)) +
    geom_line(aes(group = buffer), alpha = .2) +
    theme_minimal()
```
## map
```{r}
changeDF <- mnSalesJoin %>%
    mutate(wfDate = if_else(sale_date < ymd("2017-01-01"), "before", "after")) %>% 
    group_by(block, wfDate) %>% 
    filter(sale_price > 50000) %>%
    summarise(avgSale = mean(log(sale_price))) %>% 
    ungroup() %>% 
    tidyr::pivot_wider(names_from = wfDate, values_from = avgSale) %>% 
    mutate(change = after - before)


plutoWF %>% left_join(changeDF, by = c("Block" = "block")) %>% 
    tm_shape() +
    tm_polygons(col ="change") +
    tm_shape(wfHarlemBufferHalf) +
    tm_borders()

```


```{r}

didreg = lm(last ~ buffer * time, data = mnSalesRepeat %>% 
    #st_drop_geometry() %>% 
    filter(building_class_at_present == "R4") %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present)) %>% 
    ungroup() %>% 
                mutate(buffer = if_else(buffer == "Mile", 0, 1),
                       time = if_else(time =="Before WF", 0, 1)))
summary(didreg)
```

## panel data

```{r}

didreg = lm(last ~ buffer * time, data = mnSalesRepeat %>% 
    #st_drop_geometry() %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present)) %>% 
    filter(last < 10000000, last > 50000)  %>% 
    tidyr::pivot_wider(names_from = time, values_from = last) %>% 
    filter(!is.na(`Before WF`), !is.na(`After WF`)) %>% 
    tidyr::pivot_longer(names_to = "time", values_to = "last", -c(BL, buffer, class)) %>% 
    ungroup() %>% 
                mutate(buffer = if_else(buffer == "Mile", 0, 1),
                       time = if_else(time =="Before WF", 0, 1)))
summary(didreg)
```

```{r}

didreg = lm(last ~ buffer * time, data = mnSalesRepeat %>% 
    #st_drop_geometry() %>% 
    group_by(BL, buffer, time) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present)) %>% 
    filter(last < 10000000, last > 50000)  %>% 
    tidyr::pivot_wider(names_from = time, values_from = last) %>% 
    filter(!is.na(`Before WF`), !is.na(`After WF`)) %>% 
    tidyr::pivot_longer(names_to = "time", values_to = "last", -c(BL, buffer, class)) %>% 
    ungroup() %>% filter(class == "R4") %>% 
                mutate(buffer = if_else(buffer == "Mile", 0, 1),
                       time = if_else(time =="Before WF", 0, 1)))
summary(didreg)
```

fixed effects
```{r}
library(lfe)
library(broom)
FEDF <- mnSalesRepeat %>% 
   # st_drop_geometry() %>% 
    mutate(year = year(sale_date)) %>% 
    group_by(BL, buffer, year) %>% 
    summarize(last= last(sale_price),
              class = first(building_class_at_present),
              time = first(time)) %>% 
    filter(last < 10000000, last > 50000) %>% 
                mutate(buffer = if_else(buffer == "Mile", 0, 1),
                       time = if_else(time =="Before WF", 0, 1),
                       did = buffer * time) %>% 
    ungroup()

test <- lfe::felm(last~ did | BL + year, FEDF)

summary(test)
```

## Hedonic Pricing Model

### 
```{r}
harlemlots <- read_csv(file.path(dataDir, "modelling", "harlemSales_Attributes.csv"))
harlemlots %>% group_by(year) %>% count() 
```

## make a model per year
```{r}
valueFormula <- sale_price ~ 
    land_square_feet + gross_square_feet + year_built  + flagshipParkDist + parkDist + subwayDist +
    libDistance + popBlack/TotPop + popHisp/TotPop + avgHHsize + MedHHI + OwnerOccUnits/TotOccUnits + 
    OO_20k + OO20_49k + OO50_99k + OO50_99k + OO100_149k + OO150_299k + OO300_499k + OO_500_749k + 
    OO750_999k + OO1mil_ + permits - 1


permits <- permitsWF %>% 
    group_by(borough, Block, year) %>% 
    summarize(permits = n()) 

harlemDF <- harlemlots%>% 
    filter(sale_price < 10000000, sale_price > 50000)  %>% 
    left_join(permits %>% select(-borough)) %>% 
    left_join(mnSalesJoin %>% select(bbl, block, lot) %>% distinct(.), by = c("Block" = "block", "lot" = "lot"))

harlemDFScale <- harlemDF  %>% 
    mutate_at(vars(
                     land_square_feet , gross_square_feet , year_built  , flagshipParkDist , parkDist , subwayDist ,
                     libDistance , avgHHsize , MedHHI ,OO_20k, OO20_49k, OO50_99k, OO100_149k,OO150_299k,OO300_499k,
                     OO_500_749k, OO750_999k, OO1mil_, permits), ~(scale(.) %>% as.vector)) %>% 
    mutate(sale_price = harlemDF$sale_price) %>% 
    filter(complete.cases(.))

harlemDFModel <- harlemDFScale %>% tidyr::nest(-year)

formulaList <- list(modlog = valueFormula)

library(purrr)
formulaDF <- map2_dfr(formulaList, formulaList %>% names(), function(x,y)tibble(name = y,formula = list(x)))%>%
    tidyr::pivot_wider(names_from = name, values_from = formula)
```

```{r}
harlemDFModel <- harlemDFModel %>% rowwise() %>% 
    bind_cols(formulaDF) %>% 
    tidyr::pivot_longer(-c(year,data), names_to = "name", values_to = "formula")

modelFunc <- function(formula, data){
    mod <- lm(formula, data)
}
predictFunc <- function(mod, data)data %>% mutate(predict = as.vector(predict(mod,data)),
                                                  predictexp = exp(predict))
residFunc <- function(data)data %>% mutate(residual = sale_price - predict)
library(useful)
## glmnet
xFunc <- function(formula,data) build.x(formula, data, contrasts=FALSE, sparse=TRUE)
yFunc <- function(formula,data) build.y(formula, data) %>% as.numeric()
glmnetFunc <- function(x, y){
    set.seed(990)
    mod <- glmnet::glmnet(x=x, y=y,
                     family='gaussian', standardize = FALSE)
}
predictGlmnet <- function(mod, x)tibble(predictGLMNET = as.vector(predict(mod,x,s=0.01)),
                                        predictGLMENTexp = exp(predictGLMNET))


modList <- harlemDFModel %>% mutate(
                                lmmods = map2(formula,data, ~modelFunc(.x,.y)),
                                data = map2(lmmods, data,~predictFunc(.x,.y)),
                                data = map(data, ~residFunc(.x)),
                                x = map2(formula,data,~xFunc(.x,.y)),
                                y = map2(formula,data,~yFunc(.x,.y)),
                                glmnetMods = map2(x,y, ~glmnetFunc(.x,.y)),
                                dataGlmnet = map2(glmnetMods, x,~predictGlmnet(.x,.y)))
```

## Diagnostics




```{r}
modList$data[[1]] %>% ggplot(aes(x=residual)) + geom_histogram()
```

```{r}
harlemPLUTO <- st_read(file.path(shapeDir, "harlemPoints"))
map <- harlemPLUTO %>% inner_join(modList$data[[1]], by = c("BBL" = "bbl"))
```

```{r}
    tm_shape(wfHarlemBufferOne) + 
    tm_borders() +
    tm_shape(wfHarlemBufferHalf) + 
    tm_borders() +
    tm_shape(map)  +
    tm_symbols(col = "residual") 

```


## predict all unit prices per year

```{r}
allunitsDF <- harlemDFScale %>% select(c(land_square_feet, gross_square_feet, year_built, flagshipParkDist, parkDist, subwayDist,
                     libDistance, avgHHsize, popBlack, TotPop, popHisp, MedHHI, OwnerOccUnits, TotOccUnits, 
                     OO_20k, OO20_49k, OO50_99k, OO100_149k,OO150_299k,OO300_499k,
                     OO_500_749k, OO750_999k, OO1mil_, permits, bbl)) %>% mutate(sale_price = bbl) %>% distinct(.)

modList <- modList %>% mutate(predictData = map(lmmods,~predictFunc(.x,allunitsDF)),
                              xall = map(formula,~xFunc(.x,allunitsDF)),
                                dataGlmnetall = map2(glmnetMods, xall,~predictGlmnet(.x,.y)))
```


```{r}
test <- modList %>% select(year, predictData) %>% tidyr::unnest(predictData) %>%
    select(year, bbl, predict,predictexp) %>%     
    bind_cols(modList %>% select(dataGlmnetall) %>% tidyr::unnest(dataGlmnetall)) %>% 
    left_join(mnSalesJoin %>% select(bbl, time, buffer), by = c("bbl" = "bbl")) %>% 
    group_by(year, buffer) %>% 
    summarize(meanPriceLM = mean(predict),
              medPriceLM = median(predict),
              meanPriceGL = mean(predictGLMNET),
              medPriceGL = median(predictGLMNET))

testPlot <- test %>% tidyr::pivot_longer(names_to = "mods", values_to = "price", -c(year, buffer))
```

```{r}
testPlot %>% 
    ggplot(aes(year, price, group = mods)) +
    geom_point(aes(group = mods, color = mods, shape=buffer)) +
    geom_line(aes(group = buffer, color = mods), alpha = .2 ) +
    facet_wrap(~mods) + 
    theme_minimal()
```

# Fixed Effects with Hedonic Pricing Outcomes
```{r}
FEDFHed <- modList %>% select(year, predictData) %>% tidyr::unnest(predictData) %>%
    select(year, bbl, predict,predictexp) %>%     
    bind_cols(modList %>% select(dataGlmnetall) %>% tidyr::unnest(dataGlmnetall)) %>% 
        left_join(mnSalesJoin %>% select(bbl,buffer), by = c("bbl" = "bbl")) %>% 
     mutate(time = if_else(year < 2017, "Before WF", "After WF")) %>% 

    filter(predict < 10000000, predict > 50000,predictGLMNET < 10000000, predictGLMNET > 50000) %>% 
                mutate(buffer = if_else(buffer == "Mile", 0, 1),
                       time = if_else(time =="Before WF", 0, 1),
                       did = buffer * time) %>% 
    ungroup()

feHedLM <- lfe::felm(predict~ did | did | year + bbl, FEDFHed)

summary(feHedLM)

feHedGLM <- lfe::felm(predictGLMNET~ did | year + bbl, FEDFHed) # takes in to account residuals clustered by year

summary(feHedGLM)
```

# regular dnd regression
```{r}

didreglm = lm(predict ~ buffer * time, data = FEDFHed)
summary(didreglm)

didregGLM = lm(predictGLMNET ~ buffer * time, data = FEDFHed)
summary(didregGLM)
```

# LM plots
```{r}
FEDFHed %>% select(year, bbl, predict, time, buffer) %>% 
    ggplot(aes(x=year, y=predict, group = bbl)) +
    geom_line(alpha = .1, aes(color = time)) +
    facet_wrap(~buffer) +
    theme_minimal()
```


```{r}
FEDFHed %>% select(year, bbl, predict, time, buffer) %>% 
    ggplot(aes(x=year, y=predict)) +
    geom_hex(bins = 10) +
    facet_wrap(~buffer) +
    theme_minimal()
```

```{r}
FEDFHed %>% select(year, bbl, predict, time, buffer) %>% 
    ggplot(aes(x=year, y=predict)) +
    geom_bin2d(bins = c(5,20)) +
    facet_wrap(~buffer) +
    theme_minimal()
```


# glmnet plots
```{r}
FEDFHed %>% select(year, bbl, predictGLMNET, time, buffer) %>% 
    ggplot(aes(x=year, y=predictGLMNET, group = bbl)) +
    geom_line(alpha = .1, aes(color = time)) +
    facet_wrap(~buffer) +
    theme_minimal()
```


```{r}
FEDFHed %>% select(year, bbl, predictGLMNET, time, buffer) %>% 
    ggplot(aes(x=year, y=predictGLMNET)) +
    geom_hex(bins = 10) +
    facet_wrap(~buffer) +
    theme_minimal()
```

```{r}
FEDFHed %>% select(year, bbl, predictGLMNET, time, buffer) %>% 
    ggplot(aes(x=year, y=predictGLMNET)) +
    geom_bin2d(bins = c(5,20)) +
    facet_wrap(~buffer) +
    theme_minimal()
```


## Over buffers
 for each distance
 for each year
```{r}
## for each distance
distanceList <- as.list(seq(1320,4620, 660))

bufferFunction <- function(buffer, data, wf){
    varName  <- paste0("buffer_", buffer)
    wfBuffer <- wf %>% st_buffer(buffer)
    
    output <- data %>% 
    filter(!Block %in% c(1111, 1897)) %>% 
    sf::st_join(wfBuffer %>%mutate(!!varName := 1),join =st_within) %>%  
        st_drop_geometry() %>% 
        select(!!varName)
}

distanceBuffers <- map_dfc(distanceList, ~bufferFunction(.x, plutoWF, wfHarlem))
distanceBuffers <- distanceBuffers %>% replace(is.na(.), 0)
```


```{r}
joinBuffer <- harlemDFScale %>% select(c(land_square_feet, gross_square_feet, year_built, flagshipParkDist, parkDist, subwayDist,
                     libDistance, avgHHsize, popBlack, TotPop, popHisp, MedHHI, OwnerOccUnits, TotOccUnits, 
                     OO_20k, OO20_49k, OO50_99k, OO100_149k,OO150_299k,OO300_499k,
                     OO_500_749k, OO750_999k, OO1mil_, permits, Block, bbl))  %>% distinct(.) %>% 
    left_join(plutoWF %>% bind_cols(distanceBuffers) %>% st_drop_geometry %>% distinct(.)) %>% 
    select(starts_with("buffer_"))

modBuffer <- modList %>% 
    mutate(joinBuffer = map(year, function(x) joinBuffer)) %>% 
    mutate(bufferDF = map2(.x = predictData,.y =  joinBuffer,.f =  function(x,y) tibble(x %>% bind_cols(y))))

modBufferPlot <- modBuffer %>% select(year, bufferDF) %>% tidyr::unnest(bufferDF) %>%
    select(year, bbl, predict, starts_with("buffer_")) %>%     
    bind_cols(modList %>% select(dataGlmnetall) %>% tidyr::unnest(dataGlmnetall)) %>% 
    select(-predictGLMENTexp) %>% 
    tidyr::pivot_longer(names_to = "bufferType", values_to = "treatment", -c(year, bbl, predict, predictGLMNET)) %>% 
    group_by(year, bufferType, treatment) %>% 
    summarize(meanPriceLM = mean(predict),
              medPriceLM = median(predict),
              meanPriceGL = mean(predictGLMNET),
              medPriceGL = median(predictGLMNET))
```

```{r}
modBufferPlot %>% 
    tidyr::pivot_longer(names_to = "mods", values_to = "price", -c(year, bufferType, treatment)) %>% 
    mutate(treatment = as.factor(treatment)) %>% 
    ggplot(aes(year, price, group = mods)) +
    geom_point(aes(group = mods, color = mods, shape=treatment)) +
    geom_line(aes(group = treatment, color = mods), alpha = .2 ) +
    facet_grid(mods~bufferType, scales = "free_y") + 
    theme_minimal()+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    
```

```{r}
FEDBufferDF <- modBuffer %>% select(year, bufferDF) %>% tidyr::unnest(bufferDF) %>%
    select(year, bbl, predict, starts_with("buffer")) %>%     
    bind_cols(modList %>% select(dataGlmnetall) %>% tidyr::unnest(dataGlmnetall) %>% select(predictGLMNET)) %>% 
    filter(predict < 10000000, predict > 50000,predictGLMNET < 10000000, predictGLMNET > 50000) %>% 
    ungroup()


fedDiagFunc <- function(distance, df, wfYear = 2017, FE = TRUE, mod = "LM"){
    varName = paste0("buffer_", distance)
    
    if(mod != "LM") FEDBufferDF <- FEDBufferDF %>% select(-predict) %>% rename(predict = predictGLMNET)
    
    modDF <- FEDBufferDF %>% select(predict, !!varName, bbl, year) %>% 
             mutate(time = if_else(year < wfYear, 0, 1)) %>%
        mutate(did = time * !!as.name(varName))
    
    if(FE) feHedLM <- lfe::felm(predict~ did | bbl + year, modDF)
    else feHedLM <- lfe::felm(predict~ did, modDF)

rmse <- sqrt(mean(feHedLM$residuals^2))
}

rmseVec <- map_dbl(distanceList, ~fedDiagFunc(.x, FEDBufferDF,wfYear = 2017, FE = TRUE, mod = "GLMNET"))

modGrid <- expand.grid(distance = seq(1320,4620, 660),
            year = seq(2011,2018,1),
            model = c("LM", "GLMENT"),stringsAsFactors = FALSE)
```

```{r}
modGridList <- split(modGrid, seq(nrow(modGrid)))
rmseVec <- modGridList %>%  map_dbl(~fedDiagFunc(.x$distance, FEDBufferDF, .x$year,FE = TRUE, mod=.x$model))
modGrid <- modGrid %>% mutate(rmse = rmseVec)
```

```{r}
modGrid %>% mutate(distance = as.factor(distance)) %>% 
    ggplot(aes(year, rmse, group = model, color = model)) + 
    geom_line() +
    facet_wrap(~distance) +
    theme_minimal()+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r}
modGrid %>% mutate(distance = as.factor(distance)) %>% 
    ggplot(aes(year, rmse, group = model, color = model)) + 
    geom_line() +
    facet_grid(model~distance, scales = "free_y") +
    theme_minimal()+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### remove quarter mile before 